Research Review: \\The Extent of Adaptive Wild Introgression in Crops

### 2018-07-30 paper.tex
revised Allaby 2015 sentence again

Beyond confounding detection of progenitor taxa, extensive introgression may necessitate a more nuanced view of crop origins.
In cases like maize and potato it is important to recognize the substantial contributions of introgressing taxa to modern crops.
While these crops may have originated from a single species or subspecies, the crops as we know them today have a broader genetic base.

>>>>

Beyond confounding detection of progenitor taxa, extensive introgression may necessitate a more nuanced view of crop origins.
In cases like maize and potato it is important to recognize the substantial contributions of introgressing taxa to modern crops.
While these crops may have originated from a single species or subspecies, the crops as we know them today have a broader genetic base.
In other cases (such as barley and rice), crops appear to have arisen from the combined contributions of multiple wild or proto-domesticated crop varieties from across distant geographies.
Such reticulated evolutionary histories defy traditional centric conceptions of domestication in favor of polycentric or noncentric origins \cite{allaby2015barley}.
